Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985 - Article codes, models, and figures for replication

### 2023-08-16 Article code, models, and figures/Which Amazon Problem article codes, models, and figures.Rmd
Updated readme and article replication rmd

This file makes publicly available all the codes, models, and figures used in the article titled ["Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985"](https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639) by Livio Silva-Muller and Henrique Sposito. The article has been published open source on Environmental Politics, please check it out! Both authors contributed equally to the article. Livio is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy. Henrique is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies. If you are using this data, codes, or figures, please cite:

>>>>

This file makes publicly available all the codes, models, and figures used in the final version of the article titled ["Which Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985"](https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639) by Livio Silva-Muller and Henrique Sposito. The article has been published open source on Environmental Politics, please check it out in this [link](https://www.tandfonline.com/doi/full/10.1080/09644016.2023.2220639)! Both authors contributed equally to the article. [Livio](https://github.com/liviosilvamuller) is a PhD Candidate in Sociology and affiliated to the Albert Hirschman Centre on Democracy. [Henrique](http://henriquesposito.com/) is a PhD Candidate in International Relations and Political Sciences and affiliated to the Centre for International Environmental Studies. If you are using this data, codes, or figures, please cite:
